Security Audit of Safeplug

### 2014-01-14 bibliography.tex

@@

\bibitem{safeplug} Safeplug, \url{https://pogoplug.com/safeplug}.

\bibitem{wired} Safeplug makes it super-easy to harness Tor's anonymity at home, \url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.

\bibitem{bittech} Pogoplug launches Tor-powered Safeplug, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.

\bibitem{schneier} Schneier on Security: Tor Appliance.  \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.

\bibitem{gigaom} Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing, \url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.

\bibitem{techreview} Online Anonymity in a Box, for \$49, \url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.

>>>>

\bibitem{fingerprint1} Cai, Xiang, et al. ``Touching from a distance: Website fingerprinting attacks and defenses.'' \emph{Proceedings of the 2012 ACM conference on Computer and Communications Security (CCS)}, 2012.

\bibitem{tor} Dingledine, Roger, et. al. ``Tor: The second-generation onion router.'' \emph{USENIX Security Symposium}, 2004.

\bibitem{bittech} Halfacree, Gareth. ``Pogoplug launches Tor-powered Safeplug'' \emph{bit-tech.net} 25 November 2013, \url{http://www.bit-tech.net/news/hardware/2013/11/25/pogoplug-safeplug/1}.

\bibitem{tor2} Johnson, Aaron, et al. ``Users get routed: Traffic correlation on Tor by realistic adversaries.'' \emph{Proceedings of the 2013 ACM SIGSAC conference on Computer \& Communications Security (CCS)}, 2013.

\bibitem{fingerprint2} Kohno, Tadayoshi et. al. "Remote physical device fingerprinting." Dependable and Secure Computing, IEEE Transactions on 2.2 (2005): 93-108.

\bibitem{lighttpd} Lighttpd. \url{http://www.lighttpd.net}

@@

\bibitem{fourthparty} Mayer, Jonathan. ``FourthParty'' \url{http://fourthparty.info}

\bibitem{commercial2} Mayer, Jonathan R., and John C. Mitchell. "Third-party web tracking: Policy and technology." \emph{IEEE Symposium on Security and Privacy (SP)}, 2012.

\bibitem{gigaom} Meyer, David. ``Say hello to Safeplug, Pogoplug’s \$49 Tor-in-a-box for anonymous surfing'', \emph{GigaOm}, 21 November 2013. \url{http://gigaom.com/2013/11/21/say-hello-to-safeplug-pogoplugs-49-tor-in-a-box-for-anonymous-surfing/}.

\bibitem{commercial1} Nikiforakis, Nick, et al. "Cookieless monster: Exploring the ecosystem of web-based device fingerprinting." IEEE Symposium on Security and Privacy. 2013.

\bibitem{safeplug} Pogoplug. ``Safeplug'', \url{https://pogoplug.com/safeplug}.

\bibitem{privoxy} Privoxy. \url{https://www.privoxy.org}

\bibitem{schneier} Schneier, Bruce. ``Tor Appliance.'' \emph{Schneier on Security}, 27 November 2013. \url{https://www.schneier.com/blog/archives/2013/11/tor_appliance.html}.

\bibitem{techreview} Simonite, Tom. ``Online Anonymity in a Box, for \$49'', \emph{MIT Technology Review}, 21 November 2013. \url{http://www.technologyreview.com/news/521676/online-anonymity-in-a-box-for-49/}.

\bibitem{wired} Solon, Olivia. ``Safeplug makes it super-easy to harness Tor\'s anonymity at home,'' \emph{Wired UK}, 22 November 2013. \url{http://www.wired.co.uk/news/archive/2013-11/22/safeplug-tor}.
